%!TEX root = ../paper.tex
\subsection{Self-Reported Concerns for Wearables}
We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:

\textit{What do you think are the most likely risks associated with wearable devices?}\\[-.5cm]

This question was asked along with demographics questions (but before any IUIPC questions, which asked a lot of direct privacy-related questions, to avoid biasing the recipients). The participants were presented with a blank box to write in, with no character limit to their open-ended responses. 

Table \ref{openresponses} shows common user concerns related to wearable devices. Appendix \ref{sec:coding} details the responses categorized in each coding label. Most are related to privacy and security, but this self-report gives a sense of what broad categories of concerns are most relevant to users. This can be used to guide research in unexplored use cases. 

In addition to privacy and security in the general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware). Other concerns were orthogonal to privacy, such as long-term health effects caused from wearing the device such as cancer from EMF waves (Health), safety hazards from wearing the device, such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial).

\begin{table}[t]
\begin{center}
\begin{tabular}{|l|r|r|}
\hline
Concern &  Responses &  Frequency   \\
\hline
Privacy & 452 & 25.32\% \\
Being Unaware & 275 & 15.40\% \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & 10.70\%\\
Safety & 185 & 10.42\%\\
Social Impact &	157 & 8.80\%\\
Financial Cost & 151 & 8.46\%\\
Security &	144 & 8.07\%\\
Accidental Sharing &	69 & 3.87\%\\
Miscellaneous &	57 & 3.19\%\\
None	& 51 & 2.86\%\\
Social Stigma &	39 & 2.18\%\\
False Information & 33 & 1.85\%\\
Don't know & 31 & 1.74\%\\
Aesthetics 	& 19 & 1.06\%\\
Don't care 	& 11 & 0.62\%\\
\hline
\end{tabular}
\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
\label{openresponses}
\end{center}
\end{table}